Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-17 tsibbletalk.Rmd
re-snapshots
revised abstract

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address: Department of Statistics
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address: Department of Econometrics and Business Statistics
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  The \pkg{tsibbletalk} package can be used to interactively explore temporal data
  of nesting and crossing structures, and discover interesting periodic/aperiodic
  slices. This package implements a shared `tsibble` object that allows for
  linked brushing for coordinated views, and a shiny module that aids in wrapping
  time lines for seasonal patterns. Basic usage of functions is demonstrated
  in the article, with data examples.
preamble: |
  \usepackage{subfig}
output: rticles::rjournal_article
---

>>>>

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address: Department of Statistics
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address: Department of Econometrics and Business Statistics
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  Temporal data often has a hierarchical structure, defined by categorical variables describing different levels, such as political regions or sales products. Nesting of categorical variables produces a hierarchical structure. The \pkg{tsibbletalk} package is developed to allow a user to interactively explore temporal data, relative to the nested or crossed structures. It can help to discover differences between category levels, and uncover interesting periodic or aperiodic slices. The package implements a shared `tsibble` object that allows for
  linked brushing between coordinated views, and a shiny module that aids in wrapping
  time lines for seasonal patterns. The tools are demonstrated using two data examples: retail turnover and tourism in Australia.
preamble: |
  \usepackage{subfig}
output: rticles::rjournal_article
---

### 2020-09-17 tsibbletalk.tex
re-snapshots
revised abstract

\abstract{%
The \pkg{tsibbletalk} package can be used to interactively explore
temporal data of nesting and crossing structures, and discover
interesting periodic/aperiodic slices. This package implements a shared
\texttt{tsibble} object that allows for linked brushing for coordinated
views, and a shiny module that aids in wrapping time lines for seasonal
patterns. Basic usage of functions is demonstrated in the article, with
data examples.
}

>>>>

\abstract{%
Temporal data often has a hierarchical structure, defined by categorical
variables describing different levels, such as political regions or
sales products. Nesting of categorical variables produces a hierarchical
structure. The \pkg{tsibbletalk} package is developed to allow a user to
interactively explore temporal data, relative to the nested or crossed
structures. It can help to discover differences between category levels,
and uncover interesting periodic or aperiodic slices. The package
implements a shared \texttt{tsibble} object that allows for linked
brushing between coordinated views, and a shiny module that aids in
wrapping time lines for seasonal patterns. The tools are demonstrated
using two data examples: retail turnover and tourism in Australia.
}
